### 2018-11-26 paperreview.tex
c1

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Carlos Enrique Tisza Vargas}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
Lima, Peru \\
ctiszav@gmail.com}

}

\maketitle

\begin{abstract}
el presente trabajo compila el resultado del estudio de 10 paper relacionados con los temas de clasificacion multilabel multimodal sobre publicaciones del portal ACM.
En la actualidad hay una busqueda de nuevos metodos o combinacion  de metodos existentes para mejorar los procesos de clasificacion de variables ,
Uno de los pilares sobre los cuales estan basados los paper es en incrementar el ratio de clasificacion utilizando muchas fuentes de datos.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
En el mundo real generalmente la representación de objetos que se desean analizar se componen de multiples etiquetas y se pueden representar con multiples representaciones modales.

Por ejemplo los articulos suelen tener texto e imagenes otro ejemplo seria  de  el historial de datos de un usuario en forma de registros el cual se analiza con la finalidad de generar un perfil a este se le podria adicionar grabaciones de audios y videos con la finalidad de mejorar la predicción.

Los Sistemas de recomendación híbrido atacan el problema de analizar multiple fuentes de datos con multiple etiquetas

Procesar grandes cantidades de información y clasificarlas es un problema

Debido a la cantidad de poder de calculo que se necesita para procesar enormes bases de datos, es por eso que es necesario desaroollar tecnicas para optimizar los procesos de clasificación. aun mas cuando los procesos requieren clasificaciones en tiempo real .

Se han realizado esfuerzos para mejorar la eficacia del aprendizaje multi-etiqueta con etiquetas incompletas. Actualmente la mayoria de técnicas para el  asumen que las características de los datos de entrada estan completas.

En el mundo real los datos con etiquetas incompletas son comunes y la co-ocurrencia de caracteristicas altamente incompletas y de asignaciones de etiquetas débiles es un desafío dado que los algoritmos de multietiqueta no son directamente aplicables.

\section{Sistemas de recomendación híbridos}

\subsection{Descripción del problema}

La tienda online ASOS atrajo 174 de millones de visitantes durante diciembre de 2017 y tiene 16 millomnes de clientes activos. En todo momento tiene 85K de productos activos y aproximadamente 5k de nuevos productos entran a la tienda cada semana. a traves de los anos diferentes divisiones de la compania producen y consumen diferentes atributos de los productos algunos no se muestran al cliente final por lo tanto no estan completos y no son consistentes.

En este trabajo se muestra como se ha realizado una caracterizacion de un cojunto de atributos de productos y como se habilita la personalizacion de la expereiencia de un cliente mostrandole lo mas relevante para el.

\begin{table}[]
\centering
\caption{Representación de los atributos de los productos}
\begin{tabular}{lllll}
producto & tipo  & segmento   & patron & ... \\
A        & dress & ?          & floral & ?   \\
B        & dress & girly girl & ?      & ... \\
C        & skirt & ?          & check  & ?   \\
...      & ...   & ...        & ...  & ...    
\end{tabular}

\end{table}

\subsection{Diseño}

\subsubsection{Clasificación de imagenes}
La moda es un dominio muy visual y con la popularidad del aprendizaje profundo ya existe en la literatura bastantes enfoques para clasificar y predecir los atributos de ropa a partir de la imagen. para este caso se aplicó la red neuronal convolucional VGG16 con datos entrenados de ImageNet

\subsubsection{Clasificación de Texto}
Las redes neuronales convolucionales han demostrado tambien ser efectivas en clasificar no solo imágenes sino también
texto. Las oraciones se pueden tratar como secuencias de palabras, donde
Cada palabra a su vez puede representarse como un vector en un \textit{multidimensional
word embedding space}.

\subsubsection{Multi-modal Fusion}

Cada modelidad es procesada en diferentes redes, despues de llegar a un nivel las resultados son concatenados siguiendo capas multimodales , la politica de la red esta aprendiendo a decidir que clasificador utilizara.

En la figura 1\cite{b1} se muestra la arquitectura de una red de fusión multi-modal.

\begin{figure*}
  \includegraphics[width=\textwidth,height=4cm]{figura1.png}
  \caption{Multimodal Fusión}
  \label{fig}
\end{figure*}

\subsection{Resultados}

\begin{table}[]
\centering
\caption{Resultados}
\begin{tabular}{lllll}
		 & prec@10  & recall@10\\
Popularity        & 0.00231 & 0.00765\\
Collaborative        & 0.00277±0.00011& 0.00931±0.00036 \\
Content        & 0.00246±0.00011 & 0.00755±0.00191\\
Hybrid    & 0.00313±0.00015   & 0.00960±0.00252 
\end{tabular}
\end{table}

prec@10 recall@10
Popularity 0.00231 0.00765
Collaborative 0.00277±0.00011 0.00931±0.00036
Content 0.00246±0.00011 0.00755±0.00191
Hybrid 0.00313±0.00015 0.00960±0.00252

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} Tom Zahavy, Alessandro Magnani, Abhinandan Krishnan, and Shie Mannor. 2016.
Is a picture worth a thousand words? A Deep Multi-Modal Fusion Architecture
for Product Classification in e-commerce. arXiv preprint arXiv:1611.09534 (2016).
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2018-11-26 paperreview.tex
m2

@@
 
-prec@10 recall@10
-Popularity 0.00231 0.00765
-Collaborative 0.00277±0.00011 0.00931±0.00036
-Content 0.00246±0.00011 0.00755±0.00191
-Hybrid 0.00313±0.00015 0.00960±0.00252
+\section{A Multi-Modal Multi-Instance
+Multi-Label Deep Network with Optimal Transport}
+
+Este trabajo apunta a predecir y explorar la correlaccion simultaneamente de la etiqueta.
+se propuso usar la red M3DN modelo Multi-modal Multi-instancia Multietiqueta , que modelo una red profunda para cada modalidad, en inpone la consistencia modal en bag-level requeriendo la prediccion bag-base de diferentes modalidades deberia generar una etiqueta similar de correlacion en el mismo bag.
+
+En la red M3DN entran  bags de instances de diferentes redes profundas de modos, basado en la teroia del transporte optimo(OT), bag-label predictions  requieren predicciones de etiquetas coherentes con la métrica de la etiqueta aprendida.
+En la otra mano tomando en cuenta la incertidumbre del conocimiento previo, se moldea la exploracion de la  correlacion de las etiquetas como un problema de ground metric.
+,
+M3DN automaticamente aprende los predictores para diferentes modalidades
+
+\begin{figure*}
+  \includegraphics[width=\textwidth,height=4cm]{figura2.png}
+  \caption{Flujo de M3DN}
+  \label{fig}
+\end{figure*}
 

### 2018-12-10 paperreview.tex
ll
las

--- 2018-11-26 paperreview.tex
@@
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
+\textit{Ricardo Palma (of Aff.)}\\
 Lima, Peru \\
@@
 
+\subsubsection{Multi-Task learning with Missing Labels}
+Los datos de entrenamiento requerirían implementar una función de pérdida personalizada o enmascarar capas para evitar propagar errores cuando una etiqueta no está disponible.
+
+Se implementó la arquitectura mostrada en la figura 4, aquí los cuadros de color gris representan las entradas a la red  , entre parentesis se muestran el tamaño de la salida de cada red , en azul las capas ocultas y rojo las capas de salidad .
+
+en la practica como se ilustra en la figura se contruye un modelo para cada atributo pero todos comparten los mismos parámetros hasta laa capa de salida.
+Tambien se prepapa un conjunto de datos para cada atributo , los cuales son actualizados mediante el enjoque de descenso de gradiente(SGD) durante el entrenamiento .
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura4.png}}
+\caption{Multi-modal multi-task architecture}
+\label{fig}
+\end{figure}
+
 \subsection{Resultados}
+
+La tabla 2 muestra los resultados de los experimentos de recomendanciones , promedios y desviaciones estandares despues de 10 ejecuciones .
+Se observa que el modelo hibrido es el mas efectivo comparado con otras aproximaciones como filtrado colaborativo .
 
@@
 
-prec@10 recall@10
-Popularity 0.00231 0.00765
-Collaborative 0.00277±0.00011 0.00931±0.00036
-Content 0.00246±0.00011 0.00755±0.00191
-Hybrid 0.00313±0.00015 0.00960±0.00252
+\section{A Multi-Modal Multi-Instance
+Multi-Label Deep Network with Optimal Transport}
 
+Este trabajo el objetivo es predecir y explorar la correlacción de las etiquetas  simultaneamente.
+se propuso usar la red M3DN (modelo Multi-modal Multi-instancia Multietiqueta) que modela las redes independientes para cada modalidad e impone la  consitencia en el bag level que se utiliza para la predicción de diferentes modalidades que tienen etiquetas correlacionadas
+
+Se denomina bag a cada muestra la cual esta representada por varias instancias
+
+Se tiene N bags los cuales pueden ser positivos o negativos , además cada bag tiene k modalidades las cuales tienen un conjunto de instancias que son los datos de entrenamiento.
+
+\subsection{Transporte óptimo} 
+el transporte optimo se define como la distancia minima que existe entre dos distribuciones.
+
+\subsection{Multi-Modal Multi-instance Multi-label Deep Network (M3DN)}
+En la figura 3 se muestra las dos modalidades , el bag de 4 imagenes y el bag de 5 parrafos de texto.
+En base a la teoria del transporte optimo, M3DN adopta la distancia ooptima de transporte para medir la ccalidad de la prediccion que captura la informacion geolmetrica del esllpacio de la etiqueta subyacente  .
+
+ademas M3DN automaticamente aoprende de la correlacion entre las etiquetas de las diferentes modalidades. M3DN automaticamente aprenden los predictores de las diferentes modalidades .
+
+\begin{figure*}
+  \includegraphics[width=\textwidth,height=4cm]{figura2.png}
+  \caption{Multimodal Fusión}
+  \label{fig}
+\end{figure*}
+
+\subsection{Resutados}
+
+Comparación de los resultados (mean+std) de M3DM sobre los datos de WKG Game-Hub.
+
+ \begin{figure*}
+  \includegraphics[width=\textwidth,height=4cm]{figura5.png}
+  \caption{Resultados}
+  \label{fig}
+\end{figure*}
+
+\subsection{Exploración de Correlación de etiquetas}
+
+Teniendo en cuenta que M3DN puede aprender la correlación de la etiqueta explícitamente.
+En esta subsección, examinamos la efectividad de M3DN.
+
+La exploración se lleva a cabo en el conjunto de datos  real de
+WKG Game-Hug. Muestreamos aleatoriamente 27 etiquetas, y
+la métrica del terreno aprendida por M3DN se muestra en la Figura 4, y
+escalamos el valor original en la matriz de costos en [-1, 1]. rojo
+color indica una correlación positiva, y azul indica una correlación negativa.
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura6.png}}
+\caption{Multi-modal multi-task architecture}
+\label{fig}
+\end{figure}
 \section{Prepare Your Paper Before Styling}

### 2018-12-13 paperreview.tex
ads

@@
 La tabla 2 muestra los resultados de los experimentos de recomendanciones , promedios y desviaciones estandares despues de 10 ejecuciones .
-Se observa que el modelo hibrido es el mas efectivo comparado con otras aproximaciones como filtrado colaborativo .
+Se observa que el modelo hibrido es el mas efectivo comparado con otros enfoques como filtrado colaborativo .
 
@@
 \end{figure}
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\section{Multimodal Sentiment Analysis To Explore the Structureof Emotions}
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+Se utiliza un enfoque para el análisis de sentimientos multimodal usando redes neuronales profundas combinando el análisis visual y el procesamiento de lenguaje natural.
+el objetivp a diferencia de de otras redes donde el objetivo es predecir si unaa sentencia es positivo o negaativo aqui se el objetivo es inferir el estado emocional latente del usuario.
+Por lo tanto, nos centramos en predecir las etiquetas de palabras de emoción unidas por los usuarios a sus publicaciones de Tumblr, tratando estas "emociones autoinformadas".
+Demostramos que nuestro modelo multimodal que combina las características  , automáticamente ofrece listas de palabras sensibles asociadas con las emociones.
+Exploramos la estructura de emociones que implica nuestro modelo y la comparamos con lo que se ha publicado en la literatura de psicología, y validamos nuestro modelo en un conjunto de imágenes que se han utilizado en estudios de psicología.
+Por último, nuestro trabajo ofrece una herramienta para el auge del estudio académico de imágenes, tanto de fotografías como de mimos, en redes sociales.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+\section{La base de datos Tumblr}
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+Tumblr es un servicio de microblogging donde los usuarios publican contenido multimedia  que a menudo contiene los siguientes atributos: una imagen, texto,
+y etiquetas.
+El enfoque es que a partir de métodos de análisis de sentimientos centrados  puramente en una clasificación de positivo y negativos se usan las etiquetas de palabras de emoción como las etiquetas que deseamos predecir.
+Al considerar estas etiquetas de palabras como indicadores de emoción que esta asociado al estado mental del usuario al escribir una publicación, podemos usarlos como un proxy para la emoción autoinformada, y
+por lo tanto, un proxy para el estado emocional subyacente del usuario.
+Para construir nuestro conjunto de datos, se realizaron consultas a través del api de Tumblr buscando las  emociones que van apareciendo en las etiquetas. Las 15 emociones
+retenidas fueron aquellos con altas frecuencias relativas en Tumblr.
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura8.png}}
+\caption{Optimistic: "Recuerda que nada importa, como te puedes sentir triste o mal cuando el sol esta por salir"}
 \label{fig}
@@
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura9.png}}
+\caption{Relajado: Me encuentro ralajado con la vista impresionante}
+\label{fig}
+\end{figure}
+
+\subsection{Deep Sentiment: la red neuronal multinodos}
+Por un lado, la imagen de entrada, redimensionada a (224,224,3) se introduce en el Inicio
+red y produce un vector de tamaño 256. Por otro lado, el texto se proyecta en un espacio de alta dimensión. que posteriormente pasa por una capa LSTM con 1024
+unidades. Las dos modalidades se concatenan y se introducen en
+Una capa densa. La capa de salida de softmax final da la probabilidad
+Distribución sobre el estado emocional del uso.
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura7.png}}
+\caption{Relajado: Me encuentro ralajado con la vista impresionante}
+\label{fig}
+\end{figure}
+
+\subsection{Resultados}
+Usando texto solo, la precisión de la prueba es del 69%, casi el doble del
+La precisión del modelo de imagen, esto sugiere que en Tumblr, el texto es un
+mejor predictor de la emoción que las imágenes, como ilustramos en la fig 9 y 10
+al combinar texto e imágenes, Deep Sentiment logra un 80% de precisión con la data de  entrenamiento y 72% de precisión con los datos de prueba, superando significativamente a los modelos de solo imagen y ligeramente superior al modelo de solo texto
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura10.png}}
+\caption{Precisión con la data de entrenamiento}
+\label{fig}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura11.png}}
+\caption{Precisión con la data de prueba}
+\label{fig}
+\end{figure}
+
+\subsection{Multi-label Learning with Highly Incomplete Data via Collaborative Embedding}
+
+Se han dedicado enormes esfuerzos a mejorar la eficacia del aprendizaje multi-etiqueta con asignaciones de etiqueta incompletas.
+La mayoría de las técnicas actuales asumen que las características de entrada de las instancias de datos están completas.
+Sin embargo, la co-ocurrencia de características altamente incompletas y asignaciones de etiquetas débiles es un desafío y un problema ampliamente percibido en el aprendizaje de etiquetas múltiples del mundo real solicitudes debido a una serie de razones prácticas, incluyendo recopilación incompleta de datos, etiquetas moderadas de anotadores, etc.
+Los algoritmos de aprendizaje de etiquetas múltiples existentes no son directamente aplicables cuando las características observadas son altamente incompletas.
+En este se ataca este problema proponiendo una multi-etiqueta débilmente supervisada
+Enfoque de aprendizaje, basado en la idea de incrustación colaborativa.
+Este enfoque proporciona un marco flexible para llevar a cabo eficientemente la clasificación de etiquetas múltiples en modo transductor e inductivo
+mediante el acoplamiento del proceso de reconstrucción de características faltantes y asignaciones de etiquetas débiles en un marco de optimización conjunta.
+Es diseñado para recuperar colaborativamente información de características y etiquetas, y extraer la asociación predictiva entre el perfil de la característicay la etiqueta  multi-etiqueta de la misma instancia de datos.
+
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura12.png}}
+\caption{Collaborative Embedding: A Transfer Learning Approach}
+\label{fig}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura13.png}}
+\caption{Feature Matrix Completion}
+\label{fig}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura14.png}}
+\caption{Collaborative Embedding: A Transfer Learning Approach}
+\label{fig}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura15.png}}
+\caption{Mean (standard deviation) of transductive Macro-
+AUC of all involved algorithms on EventCat}
+\label{fig}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=\textwidth,width=9cm]{figura16.png}}
+\caption {(standard deviation) of inductive Macro-AUC of all involved algorithms on EventCat}
+\label{fig}
+\end{figure}
+
+\subsection{AnnexML:ApproximateNearestNeighborSearch forExtremeMulti-labelClassification }
+
+Los métodos de clasificación de etiquetas múltiples extremas se han utilizado ampliamente en tareas de clasificación a escala web, como el etiquetado de páginas web y la recomendación de productos.
+En este documento se presentamos un método novedoso de incrustación de gráficos llamado "AnnexML".
+En la etapa de entrenamiento, AnnexML construye un gráfico de vectores de etiqueta para el vecino más cercano al k e intenta reproducir la estructura del gráfico en el espacio de incrustación.
+La predicción se realiza de manera eficiente mediante el uso de un aproximado
+método de búsqueda de vecino más cercano que explora de manera eficiente el gráfico de vecino k más cercano aprendido en el espacio de incrustación.
+Se realizaron evaluaciones en varios conjuntos de datos de gran escala en el mundo real y se comparo el método con los últimos métodos de vanguardia.
+Los resultados experimentales muestran que nuestro AnnexML puede mejorar significativamente la precisión de la predicción, especialmente en conjuntos de datos que tienen un espacio de etiqueta más grande.
+Además, AnnexML mejora la compensación entre el tiempo de predicción y la precisión.
+Al mismo nivel de precisión, el tiempo de predicción de AnnexML fue hasta 58 veces más rápido que el de SLEEC, que es un método basado en la incorporación de tecnología de punta.
 
 \section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
 
@@
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 
